\documentclass[10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{10pt}

\begin{document}

\begin{flushright}
  \color{gray}
  \item
\end{flushright}

\vspace{-5pt}

\begin{center}
    \textbf{\Huge \scshape Pranav Rahul Digudadi} \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/DPRAHUL-2021}{\underline{github.com/DPRAHUL-2021}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/pranavrahuldigudadi/}{\underline{linkedin.com/in/pranavrahuldigudadi}} $  $
    \faIcon{envelope}
    \href{mailto:dpranavr2021@gmail.com}
    {\underline{dpranavr2021@gmail.com}}
    \faIcon{phone}
    \textbf{\underline{9885663560}} 
    % \vspace{2pt} % Adjust the spacing as needed


\end{center}

\section{Education}
\resumeSubHeadingListStart
  
  \resumeSubheading
    {Gandhi Institute of Technology and Management (GITAM)}{Nov 2022 - May 2026}
    {B.Tech Computer Science and Engineering}{GPA: 9.88/10.0}
  \resumeSubheading
    {Narayana Junior College}{Jun 2022}
    {Class 12}{GRADE: 95.6/100.0}

\resumeSubHeadingListEnd

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Java, C, Python, JavaScript, HTML, CSS, Kotlin, XML} \\
     \textbf{Frameworks}{: Tailwind CSS, Bootstrap, Streamlit} \\    
     \textbf{UI/UX Tools }{: Figma, Wix Studio, Framer} \\   
     \textbf{Tools}{: GitHub, VS Code, Android Studio, IntelliJ IDEA, OBS Studio, Canva} \\
     \textbf{Libraries \& APIs}{: pandas, NumPy, Matplotlib, Firebase, Room Database, Retrofit} \\
     \textbf{Coursework}{: OOP, Data Structures \& Algorithms, OS, Computer Networks, Mechatronics, AI-Applications}
    }}
 \end{itemize}

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Flasho - A Grocery Delivery App} $|$ \footnotesize\emph{Kotlin, MVVM, Firebase, PhonePe, Retrofit, Coroutines}}{}
    \resumeItemListStart
      \resumeItem{Created a feature-rich e-commerce application with comprehensive user and admin functionalities.}
      \resumeItem{Implemented secure user authentication using Firebase Phone Authentication.}
      \resumeItem{Integrated PhonePe for payment processing in test mode.}
      \resumeItem{Utilized MVVM architecture and Retrofit for maintainable code.}
      \resumeItem{Leveraged Firebase for real-time database operations and Coroutines for smooth asynchronous processing.}
      \resumeItem{\textbf{GitHub:} \href{https://github.com/DPRAHUL-2021/Flasho}{\textcolor{blue}{\underline{Flasho}}}}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{DPR'S Sentiment Analyser} $|$ \footnotesize\emph{Python, Streamlit, TextBlob, VADER, Matplotlib}}{}
    \resumeItemListStart
      \resumeItem{Developed an interactive web app for sentiment analysis of user-inputted text.}
      \resumeItem{Implemented sentiment analysis using TextBlob and VADER.}
      \resumeItem{Utilized Matplotlib for dynamic visualization of sentiment proportions.}
      \resumeItem{Ensured a user-friendly interface with real-time analysis using Streamlit.}
      \resumeItem{\textbf{Project Link:} \href{https://dpr-s-sentiment-analyser-o.streamlit.app/}{\textcolor{blue}{\underline{DPR'S Sentiment Analyser}}}}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Sorting Algorithm Visualizer} $|$ \footnotesize\emph{Java, Java Swing, Multithreading}}{}
    \resumeItemListStart
      \resumeItem{Developed a Java application for visualizing various sorting algorithms.}
      \resumeItem{Implemented a diverse set of sorting algorithms, including Bubble Sort, Selection Sort, Heap Sort, Insertion Sort, Merge Sort, and Quick Sort.}
      \resumeItem{Designed a UI using Java Swing for user interaction and visualization of sorting process.}
      \resumeItem{Utilized multithreading for smooth animation during sorting.}
      \resumeItem{\textbf{GitHub:} \href{https://github.com/DPRAHUL-2021/Sorting-Algorithm-Visualizer}{\textcolor{blue}{\underline{Sorting-Algorithm-Visualizer}}}}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Achievements}
\vspace{3pt}
\resumeSubHeadingListStart
  \item \item Achieved a \textbf{top-10} finish out of \textbf{128} teams in the \textbf{GDSCWOWAP Hackathon 2024}

  \item Ranked \textbf{first} in college with the \textbf{Highest CGPA}
  \item Advanced to the final round out of \textbf{150} teams in the \textbf{Smart India Hackathon 2023}
\resumeSubHeadingListEnd


\section{Student Clubs Involvement}
\resumeSubHeadingListStart

  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{COGAAN Club} $|$ \footnotesize\emph{Coder} & \\
    \small Involved in the club centered around Coding, Animation and Development & \\
  \end{tabular*}

  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Gitam Model United Nations (GMUN)} $|$ \footnotesize\emph{Graphic Designer} & \\
    \small Designed promotional materials including social media posts and posters for GMUN events & \\
  \end{tabular*}

  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{Entrepreneurship Club} $|$ \footnotesize\emph{Event Management Member} & \\
    \small Collaborated with team members to plan and execute successful club events, fostering a vibrant entrepreneurial community & \\
  \end{tabular*}

  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{GITAM Football Club} $|$ \footnotesize\emph{Player} & \\
    \small Contributed to team strategy and performance as a right midfielder. Engaged in club events and training, fostering team cohesion. & \\
  \end{tabular*}

\resumeSubHeadingListEnd



\end{document}
